Our condition that $S_\alpha u^\alpha =0$ should hold in all frames.

We now turn our attention to the precession of a gryoscope moving in an orbit in Schwarzchild spacetime. We assume that our spin starts pointing along the $r$ direction. We can see that (working in the equatorial plane):
\begin{align*}
	S^\alpha u_\alpha &= -\left(1- \frac{2M}{r}\right) S^t u^ + R S^\phi u^\phi \\
	S^t &= \frac{R^2 S^\phi u^\phi}{u^t} \left(1 - \frac{2M}{r}\right)^{-1} \\
	S^t &=  R^2 \Omega\left(10\frac{2M}{r}\right)^{-1} S^\phi
\end{align*}
If we look at the radial component:
\begin{align*}
	\frac{dS^r}{d\tau} &= -\Gamma^r_{\beta\gamma} s^\beta u^\gamma \\
	\frac{dS^\phi}{d\tau} &= -\Gamma^\phi_{\beta\gamma} s^\beta u^\gamma \\
	\frac{dS^r}{dt}\frac{dt}{d\tau} + \Gamma^r_{tt} s^t u^t + \Gamma^r_{\phi\phi} S^\phi u^\phi &= 0 \\
	\frac{dS^r}{dt}u^t + \frac{M}{R^2}\left(1- \frac{2M}{r}\right) R^2 \Omega\left(1- \frac{2M}{r}\right)^{-1}  s^t u^t + (R-2M)\Omega S^\phi u^t &= 0 \\
	\frac{ds^r}{dt} - (R-3M)\Omega s^\phi &= 0 \\
	\frac{ds^\phi}{dt} + \frac{\Omega}{R} s^r &= 0 \\
	\frac{d^2 s^\phi}{dt^2} + \left(1-\frac{3M}{r}\right)\Omega^2s^\phi &= 0
\end{align*}
Which gives us a harmonic oscilator in $\phi$ with frequency $\Omega' = \sqrt{1 - \frac{3M}{r}}\Omega$ so:
\begin{align*}
	s^r &= S_* \sqrt{1-\frac{2M}{R}}\cos\Omega' t \\
	s^\phi &= -S_*\sqrt{1-\frac{2M}{R}}\frac{\Omega}{\Omega' R}\sin\Omega' t
\end{align*}
We then after one orbit we have:
\begin{align*}
	\frac{S^r}{S_*} &= \cos \frac{2\pi \Omega'}{\Omega} \\
	\frac{S^r}{S_*} &= \cos 2\pi\sqrt{1-\frac{3M}{R}} \\
	\Delta\phi &= 2\pi \left(1-\sqrt{1-\frac{3M}{R}}\right)
\end{align*}
For small $\frac{M}{R}$ we can say:
\begin{align*}
	\Delta\phi &\approx \frac{3\pi GM}{c^2 R}
\end{align*}
Which is approximately $8.4"$ per year for earth. This has been confirmed by experiment up to $0.5$.

\subsection{Outside a slowly rotating body}
We consider here only leading order effects from the rotation. We don't consider second order effects like changes to the spherical shape of our body.
GR wull predict changes to our metric entirely from the first order impact of the spinning object.
It can be shown that:
\begin{align*}
	ds^2 &= ds_\text{Schwartzchild}^2 - \frac{4G J}{c^3 r^2} \sin^2\theta (rd\phi)(cdt) + \mathcal{O}(J^2)
\end{align*}
We have our new quantity $\frac{GJ}{c^3 r^2}$ which governs the effects of the rotation. If we are rotating with angular speed $\Omega$ we have:
\begin{align*}
	J &\propto I\Omega \\
	J &\propto mR^2\Omega \\
	J &\propto mRV
\end{align*}
So:
\begin{align*}
	\frac{GJ}{c^3 r^2} &\propto \frac{GM}{c^2 R} \frac{V}{c}
\end{align*}
We now consider the case of a radially infalling gyroscope in this metric. We additionally choose for our gyroscope to fall along the axis of rotation of our central body.
Finally we choose the direction of the gyroscope to be perpendicular to the axis of rotation.
We want to find the precession rate to leading order in $\frac{1}{c}$, which happens to be a $\frac{1}{c^3}$ contribution.
If we work in cartesian coordinates:
\begin{align*}
	ds^2 &= ds_\text{Schwartzchild}^2 - \frac{4G J}{c^3 r^2} (cdt) \frac{xdy - ydx}{r} + \mathcal{O}(J^2)
\end{align*}
We use our equation for precession now:
\begin{align*}
	\frac{dS^\alpha}{d\tau} + \Gamma^\alpha_{\beta\gamma} S^\beta u^\gamma &= 0
\end{align*}
In the Schwartzchild geometry our fators of $\frac{GM}{Pc^2r}$ will become $\frac{GM}{c^2 r} \frac{GJ}{c^3 r^2}$, which we can then ignore as the correction is too small.
Therefore we consider:
\begin{align*}
	ds^2 &= ds_\text{flat}^2 - \frac{4GJ}{c^3 r^2} (cdt) \frac{xdy - ydx}{r}
\end{align*}
We have a four velocity that should simply be $u = (u^t,0,0,u^z)$ and $s = (0,S^x,S^y,0)$.
We now need to compute our Christofel symbols:
\begin{align*}
	g_{\alpha\delta} \Gamma^\delta_{\beta]gamma} &= \frac{1}{2} \left(\partder{g_{\alpha\beta}}{x^\gamma} + \partder{g_{\alpha\gamma}}{x^\beta} - \partder{g_{\beta\gamma}}{x^\alpha}\right)
\end{align*}
And we have metric elements:
\begin{align*}
	g_{tt} &= -c^2 & g_{xx} = g_{yy} = g_{zz} &= 1 \\
	g_{tx} &= \frac{2GJy}{c^2 z^3} & g_{ty} &= -\frac{2GJz}{c^2z^3}
\end{align*}
So then our only surviving derivitives become:
\begin{align*}
	\partder{g_{tx}}{y} &= \frac{2GJ}{c^2z^3} \\
	\partder{g_{ty}}{x} &= -\frac{2GJ}{c^2z^3}
\end{align*}
And some terms relating to $z$ which we will here ignore calculating since they don't appear in our computations. We can see:
\begin{align*}
	g_{tt}\Gamma^t_{\beta\gamma} + g_{tx} \Gamma^x_{\beta\gamma} + g_{ty} \Gamma^y_{\beta\gamma} + g_{tz} \Gamma^z_{\beta\gamma} &= -c^2\Gamma^t_{\beta\gamma}
\end{align*}
Because we are looking at paths where $x=y=0$L
\begin{align*}
	\Gamma^t_{\beta\gamma} &= 0
\end{align*}
And:
\begin{align*}
	g_{xt}\Gamma^t_{\beta\gamma} + g_{xx}\Gamma^x_{\beta\gamma} + \ldots &= \Gamma^x_{\beta\gamma}
\end{align*}
So:
\begin{align*}
	\Gamma^x_{\beta\gamma} &= \frac{1}{2}\left(\partder{g_{x\beta}}{x^\gamma} + \partder{g_{x\gamma}}{x^\beta} - \partder{g_{\beta\gamma}}{x}\right)
\end{align*}
If $\beta = t$ we can say:
\begin{align*}
	\Gamma^x_{ty} &= \frac{2GJ}{c^2z^3} & \Gamma^y_{tx} &= -\frac{2GJ}{c^2z^3}
\end{align*}
So:
\begin{align*}
	\frac{dS^x}{dt} &= -\frac{2GJ}{c^2z^3}S^y & \frac{dS^y}{dt} &= \frac{2GJ}{c^2z^3} S^x
\end{align*}
