\subsection{Two-Photon states}
These states can be used to violate Bell's inequalities. Violations of these Bell's inequalaties directly implies entanglement (which in Quantum Information Theory is considered a resource that can be used).
We will begin by focusing on spectral/temporal modes.

Clearly looking at a single mode (labelled $\phi$), our two photon state is clearly $\ket{2}_\phi$. In terms of our wave packet creation operator:
\begin{align*}
	\ket{2}_\phi &= \frac{(\hat{a}^\dagger_\phi)^2}{\sqrt{2}} \vac & \hat{a}_\phi^\dagger &= \int \frac{d\omega}{2\pi} \hat{a}^\dagger(\omega)\phi(\omega)
\end{align*}
Looking now at orthogonal modes (here we choose the Hermite Gauss modes $\phi_n(t)$). We can see clearly there are many states we can generate for two photons. In general the state is:
\begin{align*}
	\ket{\psi} &= \sum_{ij} c_{ij} \hat{a}^\dagger_{\phi_i} \hat{a}^\dagger_{\phi_j} \vac
\end{align*}
Where there are extra factors of $\sqrt{2}$ in the $i=j$ terms that need to be carefully tracked here.

For a two photon state, with photons that can distinguished by another degree of freedom, we can say:
\begin{align*}
	\ket{\psi}_{1,2} &= \int \frac{d\omega_1}{2\pi}\int \frac{d\omega_2}{2\pi} \psi_{12}(\omega_1,\omega_2) \hat{a}^\dagger_1(\omega_1) \hat{a}_2^\dagger(\omega_2)\vac
\end{align*}
Where $\psi_{12}$ is our joint spectral amplitude. A factorable JSA implies will look like a circle in $\omega_1, \omega_2$ space. 
This means there's no correlations, no entanglement, and that our JSA can be written $\psi{12}(\omega_1,\omega_2) = \psi_1(\omega_1)\psi_2(\omega_2)$.
If we are in a system where we can no longer distinguish the photons, we can still have entanglement, but instead of having the photons carry the entanglement, we have the modes carrying the entanglement.
For example the state: $\ket{\psi} = c_{00} \ket{2}\ket{0} + c_{11}\ket{0}\ket{2}$ is an entangled state between the first and second mode. In fact we can have entanglement here for a single photon!

If we work with a JSA that looks more like a peapod/cigar in terms of $\omega_1,\omega_2$ then we know we have entanglement. We say this can be expressed in terms of a correlation bandwidth $\Delta_-$ and a bandwidth $\Delta_+$.
If we measure the spectrum of a single photon of our two photon system we'll see a bandwidth $\Delta_+$, but if we instead look at both photons we see that for a given $\omega_1$ our $\omega_2$ bandwidth is $\Delta_-$.

Looking at this in the temporal domain instead we have:
\begin{align*}
	\ket{\psi}_{1,2} &= \int dt_1\int dt_2 \tilde{\psi}(t_1,t_2) \hat{a}_1^\dagger(t_1)\hat{a}_2^\dagger(t_2)\vac
\end{align*}
Where we can retrieve this by taking fourier transforms. Clearly if $\psi_{12}$ is factorable $\tilde{\psi}$ will also be factorable. 
In the temporal basis the time spread of the photons are related to $\frac{1}{\Delta_-}$ while the correlations are related to $\frac{1}{\Delta_+}$.
A lack of correlation in $|\psi_{12}|^2$ does not imply a lack of correlation between the states. 
Lets say our JSA is:
\begin{align*}
	\psi_{12}(\omega_1,\omega_2) &= \psi_1(\omega_1)\psi_2(\omega_2) e^{i\omega_1\omega_2 \Delta^2}
\end{align*}
In the temporal domain for our second photon this becomes:
\begin{align*}
	\psi_1(\omega_1)\tilde{\psi}_2(t_2 + \omega_1\Delta^2)
\end{align*}
Which gives us correlations between the frequency of one photon and the time of arrival of another. Physically this state can be generated using a chirped pump into a seperable downconversion source.

Given our JSA we can always decompose this into a set of modes. It turns out there exists a special decomposition, the Schmidt decomposition, which lets us write this in terms of paired up orthogonal modes.
This is equivalent to a singular value decomposition in terms of discrerte matricies. Neither of these generalize to more than two dimensions as these decompositions are no longer unique.
We assume that our JSA is gaussian and we have central frequencies $\omega_{\{1,2\}} = \omega_{0\{1,2\}} + \nu^{\{\ ,}\ '\ ^\}$. So:
\begin{align*}
	\psi(\nu,\nu') &= \frac{1}{\sqrt{\pi\Delta_+\Delta_-}} e^{- \frac{(\nu + \nu')^2}{4\Delta_+^2} - \frac{(\nu-\nu')^2}{4\Delta_-^2}}
\end{align*}
Identifying terms in the Mehler identity:
\begin{align*}
	u &= \frac{\Delta_+ - \Delta_-}{\Delta_+ +\Delta_-} \lor \frac{\Delta_+ +\Delta_-}{\Delta_+ - \Delta_-} \\
	x &= \frac{\nu}{\sqrt{\Delta_+\Delta_-}} & y &= \frac{\nu'}{\sqrt{\Delta_+\Delta_-}} 
\end{align*}
So:
\begin{align*}
	\psi(\nu,\nu') &= \frac{1}{\sqrt{\pi\Delta_+\Delta_-}} \sum_n \sqrt{\pi}\sqrt{1-u^2} u^n \psi_n\left(\frac{\nu}{\sqrt{\Delta_+\Delta_-}}\right)\psi_n\left(\frac{nu'}{\sqrt{\Delta_+\Delta_-}}\right) \\
	\psi(\nu,\nu') &= \sum_n \sqrt{\Delta_+\Delta_-\lambda_n} \psi_n\left(\frac{\nu}{\sqrt{\Delta_+\Delta_-}}\right)\psi_n\left(\frac{nu'}{\sqrt{\Delta_+\Delta_-}}\right) & \lambda_n &= u^{2n}(1-u^2) \\
	\psi(\nu,\nu') &= \sum_n \sqrt{\lambda_n}\phi_n(\nu)\phi_n(\nu') & \phi_n(\nu) &= \frac{\psi_n\left(\frac{\nu}{\sqrt{\Delta_+\Delta_-}}\right)}{(\Delta_+\Delta_-)^\frac{1}{4}}
\end{align*}
Where $\psi_n$ are Hermite Gaussians, and $\sum_n \lambda_n = 1$.

We can define a Schmidt rank for our state:
\begin{align*}
	K &= \frac{1}{\sum_n \lambda_n^2}
\end{align*}
Where we can see for a seperable state $K=1$ and for all other states $K>1$. To better understand this quantity we take the partial trace of our state over system 2:
\begin{align*}
	\rho_1(\nu) &= \Tr_2\{\ket{\psi}_{1,2}\bra{\psi}_{1,2}\} \\
	\rho_1(\nu) &= \Tr_2\{\sum_{m,n} \sqrt{\lambda_m\lambda_n} (\ket{1}_m \bra{1}_n)\otimes(\ket{1}_m\ket{1}_n)\} \\
	\rho_1(\nu) &= \sum_{m,n} \sqrt{\lambda_m\lambda_n} (\ket{1}_m \bra{1}_n)\otimes(\ket{1}_m\ket{1}_n) \delta_{mn} \\
	\rho_1(\nu) &= \sum_{m} \lambda_m \ket{1}_m \bra{1}_m
\end{align*}
Which is a mixture of our Shmidt modes! Our purity is clearly $\sum_n \lambda_n^2$ which is one over our Shmidt rank. This Shmidt rank is therefore the number of modes needed to represent our state (approximately). 

For non-Gaussian systems we can still say this is true with a slightly different form:
\begin{align*}
	\psi(\nu,\nu') &= \sum_n \sqrt{\lambda_n} \phi_n(\nu)\psi(\nu') \\
	\int d\nu \phi_n(\nu)\phi_m^*(\nu') &= \delta_{mn} & \int d\nu \psi_n(\nu)\psi_m^*(\nu) &= \delta_{nm}
\end{align*}
Where $\psi$ and $\phi$ have no orthogonality relationship in general. We have identical modes for any system symmetric about interchange of $\nu$ and $\nu'$

It turns our that our Schmidt rank is a measure of entanglement (though it is an unbounded measure).
