After a POVM we will see that the state will change. 
The Kraus operators are somehow the square root of the POVMs we have been using, and so $\Pi_n = K_n^\dagger K_n$, and the state after measurement will be $\rho \to \frac{K_n\rho K_n^\dagger}{\sqrt{\Tr{K_n\rho K_n^\dagger}}}$
\subsection{Noisy Quantum Gates}
We represent ideal states by a ket $\ket{\psi}$ and mixed states by density operators $\rho$.
For an ideal transformation we know that these are all unitary operators. We know our operator will have to be linear for a mixed state (because QM is linear).

We can saw that by rearranging our single qubit $\rho$ into the shape of a vector of length 4, we can then say that linearity required our map to be described by a $4\cross4$ matrix, with some properties derived from our requirements on $\rho$, so:
\begin{align*}
	\mathcal{L}(\rho)^\dagger &= \mathcal{L}(\rho) \\
	\Tr{\mathcal{L}(\rho)} &= 1 \\
	\Tr{\mathcal{L}(\rho)} \geq 0
\end{align*}
Note that $\mathcal{L}$ need not be hermitian, it just must preserve the Hermiticity of matrices it operators on. We can see that $\mathcal{L}$ has some $D^2\cross D^2$ representation.
Looking at the first condition we see it restricts us to 12 real numbers.

For pure states $\ket{\psi}_{AB}$, we say this is a product state if and only if $\exists \ket{\tilde{\psi}}_A,\ket{\tilde{\phi}}_B: \ket{\psi}_{AB} = \ket{\tilde{\psi}}_A \otimes\ket{\tilde{\phi}}_B$. Otherwise it is in an entangled state.
We measure the level entanglement via:
\begin{align*}
	\rho_A &= \Tr_B \ket{\psi}_{AB}\bra{\psi}_AB \\
	\Tr{\rho_A} = 1 &\to \text{Product} \\
	\Tr{\rho_A} < 1 &\to \text{Engangled}
\end{align*}

We now want to consider our system in a mixed state $\rho_{AB}$. We can say our product state is defined by:
\begin{align*}
	\exists \rho_A,\rho_B : \rho_{AB} &= \rho_a\otimes\rho_B
\end{align*}
We can test this by saying:
\begin{align*}
	\tilde{\rho_A} &= \Tr_B \rho_{AB} \\
	\tilde{\rho_B} &= \Tr_A \rho_{AB} \\
	\rho_{AB} = \rho_A \otimes \rho_B &\to \text{Product}
\end{align*}
If this is not a product state it is still not necessarily an entangled state. We say $\rho_{AB}$ is separable if and only if:
\begin{align*}
	\rho_{AB} &= \sum_i p_i \rho_A^{(i)}\otimes \rho_B^{(i)} & 
	\sum_i p_i &= 1
\end{align*}
While any non-separable state is called an entangled state. Here product states are a type of separable states.

Tests to determine if we are in a separable state scale exponentially with the number of qubits. Alternatively we can have reasonable certainty in whether or not this is a separable state by using a quantum measurement on our system.

We can instead say this is a sum over pure states:
\begin{align*}
	\rho_j q_j \ket{\psi_j}_A\bra{\psi_j}_A \times \ket{\phi_j}_B\bra{\phi_j}_B
\end{align*}

We say that the set of all states $\rho_{AB}$ is a convex set, which means if $\rho_1$ and $\rho_2$ are in the set, then all linear combinations $p\rho_1 + (1-p)\rho_2$ are in the set for all $0\leq p \leq 1$.
Clearly the set of separable states much also be a convex set. It turns out that the set of entangled states is not a convex set, since the separable states remove a convex section of our set, and not one that is on the border of our set.

We can prove the entangled states are not convex by combining two entangled states to generate a separable states:
\begin{align*}
	\ket{\psi^\pm} &= \frac{1}{\sqrt{2}}\left(\ket{00} \pm \ket{00}\right) \\
	\rho_{AB} &= \frac{1}{2} \ket{\psi^+}\bra{\psi^+} +\frac{1}{2} \ket{\psi^-}\bra{\psi^-} \\
	\rho_{AB} &= \frac{1}{4}\left(2\ket{00}\bra{00} + 2\ket{11}\bra{11}\right) \\
	\rho_{AB} &= \frac{1}{2} \unit
\end{align*}
Which is a separable state constructed from two entangled states. Therefore the set of entangled state must not be convex. Additionally the boundary of our set of states are the pure states. Additionally we can find states that are mixtures of two states on the boundary.
